Parameter estimation

### 2023-05-31 SFE-article/Sections/Thermo_imp.tex

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The fluid density based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state}
		\label{fig: SFE_Properties}
	\end{figure*}

@@

	To address this issue, the correlations of transport coefficients are either empirical or based on some theoretical foundation. Chapman-Enskog's theory (presented in \citet{Chapman1991}) for transport properties of dense gases based on the distribution function is a popular theoretical approach. However, the Chapman-Enskog theory was developed for rigid spherical molecules and modifications are required to apply it to real gases. Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998} and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST). A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_mu}.

@@

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\caption{Viscosity obtained based on different correlations } 
		\label{fig: SFE_Properties_mu}
	\end{figure*}

	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_kt}. The presented figures show regions around the critical point where the singularity is present. Similarities between specific heat and thermal conductivity can be observed. The NIST correlation (\citet{Huber2016}) captures the singular behaviour of thermal conductivity around the critical point. The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
		\caption{Thermal conductivity obtained based on different correlations }
		\label{fig: SFE_Properties_kt}
	\end{figure*}

>>>>

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The fluid density based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat of $CO_2$ based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
			\caption{The enthalpy of $CO_2$ based on the Peng-Robinson equation of state (\color{red}FONT SIZE)}
			\label{fig: SFE_Properties_h}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 1.5cm 4.0cm  14cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}
			\caption{Thermal conductivity obtained based on Laesecke correlation}
			\label{fig: SFE_Properties_Viscosity}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.5cm 2.8cm 14.3cm 21.4cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity obtained based on Huber correlation}
			\label{fig: SFE_Properties_Thermal}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state}
		\label{fig: SFE_Properties}
	\end{figure*}

@@

	To address this issue, the correlations of transport coefficients are either empirical or based on some theoretical foundation. Chapman-Enskog's theory (presented in \citet{Chapman1991}) for transport properties of dense gases based on the distribution function is a popular theoretical approach. However, the Chapman-Enskog theory was developed for rigid spherical molecules and modifications are required to apply it to real gases. Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998} and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST). A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_Viscosity}.

@@

	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_Thermal}. The presented figures show regions around the critical point where the singularity is present. Similarities between specific heat and thermal conductivity can be observed. The NIST correlation (\citet{Huber2016}) captures the singular behaviour of thermal conductivity around the critical point. The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.
